Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-03-10 WSSSPE4_report/WSSSPE4_report.tex
a few edits to paper section

The 12 excellent submissions resulting in 10-min talks (four idea papers, three position papers, two experience papers and three demos) address a wide range of topics around sustainability for software in science. They cover three main areas: 
\begin{enumerate}
\item The specifics of the academic environment for software development and for so-called research programmers or research software engineers;
\item The characteristics and needs of research software in general such as  the lifecycle of software in science, preservation, curation, sharing and reproducibility challenges;
\item Lessons learned from or visions for use cases of scientific software and communities working with and/or on a software package.
\end{enumerate}

>>>>

The 12 excellent submissions resulted in 10-min talks (four idea papers, three position papers,
two experience papers, and three demos) that addressed a wide range of topics around
sustainability for software in science. They covered three main areas:
\begin{enumerate}
\item The specifics of the academic environment for software development and for so-called
research programmers or research software engineers;
\item The characteristics and needs of research software in general such as the lifecycle of
software in science, preservation, curation, sharing, and reproducibility challenges; and
\item Lessons learned from or visions for use cases of scientific software and communities
working with and\slash or on a software package.
\end{enumerate}
